Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Fixing IBM section. References #30. References #31. Please @fergunet review and close corresponding issue

Main services offered by IBM can be divided into three categories:

\begin{itemize} 
	\item \textit{Mobile Enterprise Services}: Is offered as an integrated solution for smartphones, and tablets as well, but then it is divided in different subservices that the company has to acquire separately. Some of them are related to cloud computing, such as events and log management as a cloud security service, cloud backup, or the so-called `hosted vulnerability management'. The last one is specially interesting for the scope of this paper, given the fact that it seems to implement one of the most important advantages of the MUSES system, the self-adaptation. IBM performs deep scans over the security incidents data, either by computer forensics analysis, if the incident happened, or by normal data, if the device was enough secure. They claim in their website that they are able to recognise new vulnerabilities - or threats - with enough accuracy. The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts. Another difference is the fact that IBM software is not open source as MUSES system is. Then, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.
	\item \textit{Hosted Mobile Device Security Management}: This is a particular service of the Mobile Enterprise Services. It includes itself a number of subservices, going from tools to make easy to develop secure mobile apps, to an interface for managing the devices in the system, checking their configuration security level. As in the previous case, they are offered by IBM as `services', but these are included as default features in the MUSES system.
	\item \textit{Enterprise Wireless Networks}: Devoted to provide secure channels for communications. This is related to ensuring employees that any connection they might perform to access company assets, is properly secured, at the time it delivers the expected performance. Thus, this service is, in some sense, adaptive to the situation, yet only in terms of a secure connection and not evolving the security policies, like MUSES. 
\end{itemize}

%FERGU: HABLANDO DE LOS PRODUCTOS
{\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} is a set of mobile applications and services, based in big data analytics and cloud computing. It includes several products, such as a framework for app development (MobileFirst Platform), a Platform as a Service (BlueMix) or a threat detection system (Trusteer Rapport). %FERGU: sí, es rApport, no rEpport, no lo cambiéis :P
 However, the most interesting one with respect to this work scope, is {\em MobileFirst Protect}. This product, formerly known as {\em MaaS360} \footnote{\url{http://www.maas360.com/}}, is a MDM (Mobile Device Management) software to securize, monitor and manage mobile devices.  It uses a web portal in order to centralize the security and control policies. This allows the deployment of applications or backups, among other possibilities.
%----------------------------------------------------------------------------

@@

Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation, as they are not being successful in spite of their features. On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}. 
On the other hand, Samsung revealed at the Barcelona Mobile World Congress 2013 the KNOX application \cite{Samsung_mwc13}, which was expected to be available for its last Galaxy smartphone generation. Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still remained delayed until it was apparently found insecure \cite{Samsung_insecure}. Finally, Samsung decided to collaborate with Google in Android Work \cite{Samsung_android} (see Section \ref{subsec:androidwork}).

>>>>

Main services offered by IBM can be divided into three categories: Mobile Enterprise Services, Hosted Mobile Device Security Management, and Enterprise Wireless Networks. However, here we only discuss the former, because it is the only one related to BYOD. Mobile Enterprise Services is offered as an integrated solution for smartphones and tablets as well, but then it is divided in different subservices that the company has to acquire separately. Some of them are related, to cloud computing. Among them, there is one which is interesting for the scope of this paper, the so-called `hosted vulnerability management'. This subservice seems to implement one of the most important advantages of the MUSES system, the self-adaptation. IBM performs deep scans over the security incidents data, either by computer forensics analysis, if the incident happened, or by normal data, if the device was enough secure. They claim in their website \footnote{\url{http://www-935.ibm.com/services/us/en/it-services/security-services/vulnerability-management/}} that their tool is able to recognise new vulnerabilities - or threats - with enough accuracy. The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts. Another difference is the fact that IBM software is not open source as MUSES system is. Then, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.

%FERGU: HABLANDO DE LOS PRODUCTOS
IBM also offers some products related to BYOD security. {\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} is a set of mobile applications and services, based in big data analytics and cloud computing. It includes several products, such as a framework for app development (MobileFirst Platform), a Platform as a Service (BlueMix) or a threat detection system (Trusteer Rapport). %FERGU: sí, es rApport, no rEpport, no lo cambiéis :P
 However, the most interesting one with respect to this work scope, is {\em MobileFirst Protect}. This product, formerly known as {\em MaaS360} \footnote{\url{http://www.maas360.com/}}, is an MDM (Mobile Device Management) software to secure, monitor, and manage mobile devices. It uses a web portal in order to centralise the security and control policies. This allows the deployment of applications or backups, among other possibilities. However, MobileFirst Protect seems a typical MDM tool, which just applies the existing set of security policies. No further risk and trust analysis is performed, neither is included a refinement of the rules derived from the policies.
%----------------------------------------------------------------------------

@@

Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation, as they found problems in the market in spite of their features. On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}.
On the other hand, Samsung revealed at the Barcelona Mobile World Congress 2013 the KNOX application \cite{Samsung_mwc13}, which was expected to be available for its last Galaxy smartphone generation. Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still remained delayed until it was apparently found insecure \cite{Samsung_insecure}. Finally, Samsung decided to collaborate with Google in Android Work \cite{Samsung_android} (see Section \ref{subsec:androidwork}).
